Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-09-06 inst/doc/nonparametric-bayes.Rmd
Updated nonparametric-bayes.Rmd

@@

We demonstrate how nonparametric Bayesian models can provide robust,
nearly-optimal solutions to decision making under uncertainty when
_we don't know the correct model_ to use.

While methods that account
for _parametric_ uncertainty can be very successful with the right model,
structural uncertainty of not knowing what model best approximates the 
dynamics poses considerably greater difficulty.

Non-parametric Bayesian
methods offer a promising statistical approach for predictive modeling
of ecological dynamics in regions of state space where the data is
adequate, while at the same time offering more flexible patterns with
greater uncertainty outside the observed data. This contrasts from simple
parametric models which provide relatively constant level of uncertainty
in regions with and without adequate data. The consequence of such
misplaced confidence outside the data can lead to highly undesirable
results that may be avoided with the more flexible non-parametric
Bayesian approach.

>>>>

We address

@@

Further, the data on which a model has been parameterized frequently 
fails to cover the possible state-space over which management decisions 
must operate.  Consequently a model do well in the region of state-space
in which it was estimated, but give erroneous confidence to predictions
outside of that region.

This problem is keenly felt in any system in which a manager may fear
crossing a threshold, or tipping point. The tipping point, if it exists 
at all, will lay outside the observed range of the observed data.

We demonstrate how nonparametric Bayesian models can provide robust,
solutions to decision making under uncertainty without knowing the 
structural form of the true model.

<!--
While methods that account for _parametric_ uncertainty can be very 
successful with the right model,
structural uncertainty of not knowing what model best approximates the 
dynamics poses considerably greater difficulty.  
-->
